---
title: "Spotify Data Analysis in R"
author: "Karlo Lukic"
date: "`r format(Sys.time(), '%d/%m/%y')`"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    highlight: zenburn
    df_print: kable
    theme: default
    toc_depth: 4
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=F}
knitr::opts_chunk$set(
  echo = T, comment = "", warning = F, message = F,
  # added for better plot rendering in HTML output
  # alternatively, change each base_size to e.g. 12
  # more info: https://benjaminlouis-stat.fr/en/blog/2020-05-21-astuces-ggplot-rmarkdown/
  fig.width = 6,
  fig.asp = 0.8,
  out.width = "80%"
)
```

# Packages

```{r, error=F, warning=F, message=F}
library(data.table) # wide data manipulation
library(tidyverse) # long data manipulation
library(stringr) # string (character) manipulation
library(lubridate) # date manipulation
library(ggplot2) # static data visualization
library(GGally) # static data visualization
library(psych) # summary statistics
library(skimr) # summary statistics
library(gganimate) # dynamic data visualization
library(highcharter) # dynamic data visualization
library(plotly) # dynamic data visualization
library(scales) # static data visualization
library(knitr) # tables
library(janitor) # easy renaming of variables
library(ggcorrplot) # correlation plot
library(caret) # split train/test data
library(equatiomatic) # print model equation
library(stargazer) # classic to describe models
library(modelsummary) # modern to describe models
```

# Saved functions, shortcuts, variables…

```{r}
# re-write default digit/scipen print
options(digits = 3, scipen = 10000)

# save path to data folder: data_folder
data_folder <- file.path("/Users/karlo/Google Drive/TechAcademy/Product Development/6-SoSe21/Projekt/data")

# define colors: my_color
# note: https://usbrandcolors.com/spotify-colors/
my_color <- "#1E76B4" # matplot blue
spotify_green <- "#1DB954"
spotify_black <- "#191414"
spotify_black <- "#191414"

# set default ggplot2 theme:
# theme_set(theme_minimal(base_size = 8))

# set default ggplot2 coloring scale
# options(ggplot2.continuous.colour="viridis")

# set defualt ggplot2 font sizes (smaller images)
# theme_set(theme(text = element_text(size = 10)))
# theme_set(theme_classic(base_size = 5))
# theme_set(theme_minimal(base_size = 5))
# theme_set(theme_gray(base_size = 5))

# ggplot2 shortcuts
center_title <- theme(plot.title = element_text(hjust = 0.5))

# define line separator for a table: std_line
# std_line = officer::fp_border(color="black", width = 1)

# default DT options
options(DT.options = list(pageLength = 5, dom = "t"))
```

# Part A: Exploratory Data Analysis (Beginners + Advanced)

## Data: Kaggle Data

### 1. Getting Started

#### 1.1. Read in data, show data, give summary of data (mean, count, ...)

```{r, results="asis"}
# load song_features.csv: spotify_song_features_DT
spotify_song_features_DT <- fread("data/song_features.csv", drop = "V1")
head(spotify_song_features_DT)
```


```{r}
# load spotify_songs.csv: spotify_songs_DT
spotify_songs_DT <- fread("data/spotify_songs.csv", drop = "V1")
head(spotify_songs_DT)
```


```{r}
glimpse(spotify_song_features_DT)
```

```{r}
glimpse(spotify_songs_DT)
```

```{r}
describe(spotify_song_features_DT, 
  quant=c(.25, .75), # add quantiles
  skew = F # omit skeweness and kurtosis
)
```
```{r, eval=F, include=F}
# alternatively via {skimr}
skim(spotify_song_features_DT)
```


#### 1.2. Compute column `duration_minutes` from `duration_ms`


```{r}
# convert duration in ms to sec: 1 sec = 1,000 ms
# note: knitr does not like "in place modification"
spotify_songs_DT <- spotify_songs_DT[, duration_sec := duration_ms / 1000]

# convert duration from sec to min: 1 min = 60 ms
spotify_songs_DT <- spotify_songs_DT[, duration_min := duration_sec / 60]

# reveal changes
spotify_songs_DT[1:6, .(name, duration_ms, duration_sec, duration_min)]
```

#### 1.3. Compute mean/std of `duration_minutes`, which song has the longest duration?

```{r}
spotify_songs_DT[, .(mean_duration_min = mean(duration_min), 
                     sd_duration_min = sd(duration_min))]
```


```{r}
spotify_songs_DT[max(duration_min), .(duration_min, artists, name)]
```


#### 1.4. Plot histogram of song durations in seconds


```{r}
p <- ggplot(spotify_songs_DT, aes(duration_sec)) + 
  geom_histogram(bins = 800, color = spotify_green) +  # bins = 800 => produces similar image as matplotlib
  coord_cartesian(xlim = c(0,1000)) + # range of 0-1000 (without removing the values)
  labs(title = "Histogram of song duration",
       x = "song duration (sec.)") +  # remove x-, y-axis labels
  center_title
p

# interactive?
# ggplotly(p, tooltip = "x")
```

### 2. Time Series: How did songs change over the years?

#### 2.1. Streaming leads to shorter songs? Group-By: song duration over years


```{r, message=F}
# data.table
avg_song_duration_DT <- spotify_songs_DT[, .(mean_duration_min = mean(duration_min)), by=year]

# tidyverse
avg_song_duration_tbl <- spotify_songs_DT %>% 
  group_by(year) %>% 
  summarise(mean_duration_min = mean(duration_min))

# plot it
p <- ggplot(avg_song_duration_tbl, aes(year, mean_duration_min)) + 
  geom_line(col = spotify_green) + 
  labs(title = "Development of song duration over time", 
       x = "", y = "duration (min)") +
  theme_classic() + 
  center_title
p

# interactive?
# ggplotly(p)
```

#### 2.2. Merge songs with song_features on id

```{r}
# data.table: spotify_DT
spotify_DT <- spotify_songs_DT[spotify_song_features_DT, on = .(id)]

# tidyverse: spotify_tbl
spotify_tbl <- spotify_songs_DT %>% 
  left_join(spotify_song_features_DT, by="id") %>% 
  as_tibble()

# reveal
glimpse(spotify_DT)
```


#### 2.3. Compare how features like `acousticness`, `danceability`, `energy`, `valence`, `speechiness`, and `instrumentalness` changed over time


```{r}
# data.table: features_DT
features_DT <- spotify_DT[, lapply(.SD, mean), 
           .SDcols = c("acousticness", "danceability", "energy", "instrumentalness"), 
           by = year]

# reshape to long format: features_long_DT
features_long_DT <- melt(features_DT, id.vars = "year", 
     measure.vars = c("acousticness", "danceability", "energy", "instrumentalness"))

# tidyverse: features_tbl
features_tbl <- spotify_tbl %>% 
  group_by(year) %>% 
  summarise_at((c("acousticness", "danceability", "energy", "instrumentalness")), mean)

# reshape to long format: features_long_tbl
features_long_tbl <- features_tbl %>% 
  gather(acousticness, danceability, energy, instrumentalness, key = "variable", value = "value")

# plot
p <- ggplot(features_long_tbl, aes(year, value, color=variable)) + 
  geom_line() + 
  labs(title = "Music features over time", x = "", y = "") + 
  theme_bw() + 
  theme(legend.title = element_blank(),
        # legend.position = c(.89, .84),
        # legend.box.background = element_rect(colour = "black"),
        # legend.text = element_text(size = 7)
        ) +
  center_title + 
  scale_color_brewer(palette="Dark2") # change colors
p


# interactive?
# ggplotly(p)
```

#### 2.4. For Advanced: Radar plot (aka spider plot or polar plot) over time


```{r, eval=T}
# subset data: spider_DT
spider_DT <- spotify_DT[, .(year, valence, acousticness, danceability, energy, speechiness, instrumentalness)]

# convert tempo to var between 0-1
# spider_DT[, tempo := tempo / max(tempo)]

# group by release_year, get means of: 'acousticness', 'danceability', 'energy', 'tempo', 'speechiness', 'instrumentalness' 
spider_DT <- spider_DT[, lapply(.SD, mean), 
   .SDcols = c('acousticness', 'danceability', 'energy', 'valence', 'speechiness', 'instrumentalness'),
   by = "year"]

# melt DT
spider_DT <- melt(spider_DT, id.vars = "year")

# final plot
fig <- spider_DT %>%
  plot_ly(
    type = 'scatterpolar', 
    mode = "markers", # avoid warning
    r = ~value,
    theta = ~variable,
    fill = 'toself',
    frame = ~year,
    marker = list(color = spotify_green)
  )
fig <- fig %>%
  layout(title = 'Development of Selected Features Over Time<br>', # title?
         polar = list(
           radialaxis = list(
             visible = T, 
             range = c(0,1)
           )
         ),
         showlegend = F
  )
fig <- fig %>% 
  animation_opts(
    frame = 120, easing = "elastic" # faster transition
  )

fig
```



### 3. Artists

#### 3.1. Bar plot with artists with most songs

```{r}
# data.table: artists_DT
artists_DT <- spotify_DT[, .N, by=artists][order(N, decreasing = T)][1:15]

# tidyverse: artists_tbl
artists_tbl <- spotify_tbl %>% 
  group_by(artists) %>% 
  count(sort = T) %>% 
  head(15)

# plot
p <- ggplot(artists_tbl) +
    aes(x = reorder(artists, n), weight = n) +
    geom_bar(fill = spotify_green) +
    labs(x = "", y = "", 
         title = "15 artists with most songs") +
    coord_flip() +
    theme_classic() + 
    center_title
p

# interactive?
# ggplotly(p, tooltip = "n")
```


#### 3.2. For Advanced: Map with top songs in each country

```{r}
# prepare data: weekly_charts_DT
weekly_charts_DT <- fread("data/weekly_charts.csv", drop = "V1")

# rename all vars snakecase
weekly_charts_DT <- weekly_charts_DT %>% 
  rename_with(~ tolower(gsub(" ", "_", .x, fixed = TRUE)))

# get each country's top song
top_song_by_country_tbl <- weekly_charts_DT %>%
  group_by(country) %>%
  filter(position == 1)

# add three-letter ISO code
iso_3_DT <- fread("https://raw.githubusercontent.com/lukes/ISO-3166-Countries-with-Regional-Codes/master/all/all.csv",
                  select = c("name", "alpha-2", "alpha-3"), 
                  col.names = c("country_name", "country", "iso_3"))
# iso_3_DT

# join
top_song_by_country_tbl <- top_song_by_country_tbl %>% 
  left_join(iso_3_DT, by = "country")

# country to country-color-id
top_song_by_country_tbl <- top_song_by_country_tbl %>% 
  mutate(country_id = as_factor(country)) %>% 
  # to unique ID
  mutate(country_id = as.numeric(country_id)) 

# color boundaries between countries
l <- list(color = toRGB("white"), width = 0.5)

# specify map projection/options
# note: goes into layout() in next step
g <- list(
  showframe = F,
  showcoastlines = T,
  coastlinecolor = toRGB("gray90"),
  showland = T,
  landcolor = toRGB("grey90"),
  projection = list(type = 'Mercator')
)

# plot
top_song_by_country_tbl %>% 
  plot_ly(type = "choropleth", 
          # ISO 3 code column
          locations = ~ iso_3, 
          # color by id
          z = ~country_id,
          # text on hover
          text = paste0("Top Song in ", 
                        top_song_by_country_tbl$country_name, 
                        " was \"", 
                        top_song_by_country_tbl$track_name, 
                        "\" by ", 
                        top_song_by_country_tbl$artist),
          hoverinfo = 'text', 
          # colorscale='Rainbow',
          reversescale = T,
          marker = list(line = l)) %>% 
  # hide id legend
  hide_colorbar() %>%
  # layout options
  layout(title = "Top Spotify Song per Country", 
         geo = g)
```

### 4. Pairplot: Artist Comparison

#### 4.1. Look for three different artists and compare the features of the songs with a pairplot

```{r, message=F}
# TODO: 
# data.table
# subset 3 artists and 4 features: acousticness, danceability,instrumentalness,liveness
spotify_subset_DT <- spotify_DT[
  artists %in% c("Bob Dylan", "Nirvana", "Eminem"),
  .(acousticness, danceability, instrumentalness, liveness, artists
  )
]

# tidyverse
spotify_subset_tbl <- spotify_DT %>%
  filter(artists %in% c("Bob Dylan", "Nirvana", "Eminem")) %>%
  select(acousticness, danceability, instrumentalness, liveness, artists)

# plot
p <- ggpairs(spotify_subset_tbl, 
        columns = 1:4, 
        title = "Pairplot of 3 Artists",
        aes(col=artists), 
        progress = F, # no need for progress bar
        legend = 1, 
        # better aesthetics
        diag = list(continuous = wrap("densityDiag", alpha=0.3), combo = "facetdensity"),
        upper = list(continuous = wrap("points", alpha = .3, size = .8)),
        lower = list(continuous = wrap("points", alpha = .3, size = .8))
) + 
  center_title
p
```

#### 4.2. Look at the proposed gallery and look for a plot that you could use to visualize an aspect of the Spotify data and generate a plot

* Go to [r-graph-gallery](https://www.r-graph-gallery.com/index.html) look for a plot which could be used to visualize an aspect of the Spotfiy data and generate a plot
* e.g. [Loudness war](https://en.wikipedia.org/wiki/Loudness_war)

```{r, eval=T, include=T}
# start with static plot: p
p <- spotify_DT[, .(avg_loudness = mean(loudness)), by=year] %>% 
  ggplot(., aes(x=year, y=avg_loudness)) + 
  geom_line(color = spotify_green) + 
  labs(y = "average loudness of songs", x = "", title = "Illustration of loudness wars",
       caption = "Notes: Peak reached in 2008 with Metallica's Death Magnetic album.") +
  scale_x_continuous(n.breaks = 10) +
  scale_y_continuous(n.breaks = 10) +
  theme_bw() +
  center_title
p
```


#### 4.3. What is the message of your plot? What does it show?

* Increase in loudness of songs over the time-span

## Data: Personal Spotify Data

```{r}
# load data: personal_spotify_DT
personal_spotify_DT <- fread("data/personal_data.csv") %>% 
  janitor::clean_names()
personal_spotify_DT[1:6]
```


## 5.1. Data preparation

```{r}
# convert end_time to date_time (dt) var: end_time_dt
class(personal_spotify_DT$end_time) # char
personal_spotify_DT <- personal_spotify_DT[, end_time_dt := ymd_hm(end_time)]
class(personal_spotify_DT$end_time_dt) # POSIXct, POSIXt
```

```{r}
# split end_time_dt to multiple cols: year, month, day, hour, minute …
personal_spotify_DT <- personal_spotify_DT[, `:=`(year_int = year(end_time_dt),
                  month_int = month(end_time_dt),
                  month_long_char = month(end_time_dt, label=T, abbr=F),
                  day_int = day(end_time_dt),
                  # note: add week day just for fun
                  weekday_int = wday(end_time_dt),
                  weekday_long_char = wday(end_time_dt, label=T, abbr=F),
                  hour_int = hour(end_time_dt),
                  minute_int = minute(end_time_dt))]
personal_spotify_DT[1:6]
```

```{r}
# convert ms_played to min_played: min = sec / 60
# note: duration is always expressed in seconds
personal_spotify_DT <- personal_spotify_DT[, min_played_int := (ms_played / 1000 / 60)]
```


```{r}
# create a date var (useful for time-series): date_dt
personal_spotify_DT <- personal_spotify_DT[, date_dt := make_datetime(year_int, month_int, day_int)]
```


```{r}
# create song counter dummy variable
personal_spotify_DT <- personal_spotify_DT[, played_song_int := 1L]
```


```{r}
# convert some chars to factors: {varname}_fct
glimpse(personal_spotify_DT)
personal_spotify_DT <- 
  personal_spotify_DT[, `:=`(artist_name_fct = as_factor(artist_name),
                  track_name_fct = as_factor(track_name),
                  month_long_fct = as_factor(month_long_char),
                  weekday_long_fct = factor(weekday_long_char, # needs re-level due to ggplot2 defaults
                                            levels = c( "Monday", "Tuesday",
                                                        "Wednesday", "Thursday", 
                                                        "Friday", "Saturday", 
                                                        "Sunday")))]
glimpse(personal_spotify_DT)
```


```{r}
# assign each track a unique ID
# note: useful for finding top songs
personal_spotify_DT <- 
  personal_spotify_DT[, song_id_int := .GRP, by=track_name]
personal_spotify_DT[1:6, .(song_id_int, track_name)]
```

```{r}
# assign each track number of times it was played
# note: useful for finding top songs
personal_spotify_DT[, n_times_song_played_int := .N, by = track_name]
personal_spotify_DT[1:6, .(track_name, n_times_song_played_int)]
```


```{r}
# add 4 subsets for a day via: https://learnersdictionary.com/qa/parts-of-the-day-early-morning-late-morning-etc
# create a new var: time_of_day_fct
# morning (05:00-11:59), afternoon (12:00-16:59), evening (17:00-20:59), night (21:00-04:59)
morning_char_vec <- "morning (5-11h)"
afternoon_char_vec <- "afternoon (12-16h)"
evening_char_vec <- "evening (17-20h)"
night_char_vec <- "night (21-4h)"
# personal_spotify_DT[, .(end_time, hour_int, minute_int)]
personal_spotify_DT <- personal_spotify_DT[hour_int %between% c(5, 11), time_of_day_char := morning_char_vec]
personal_spotify_DT <- personal_spotify_DT[hour_int %between% c(12, 16), time_of_day_char := afternoon_char_vec]
personal_spotify_DT <- personal_spotify_DT[hour_int %between% c(17, 20), time_of_day_char := evening_char_vec]
personal_spotify_DT <- personal_spotify_DT[hour_int %between% c(21, 23), time_of_day_char := night_char_vec]
personal_spotify_DT <- personal_spotify_DT[hour_int %between% c(0, 4), time_of_day_char := night_char_vec]
personal_spotify_DT <- personal_spotify_DT[, time_of_day_fct := factor(time_of_day_char,
                                       levels = c(morning_char_vec, afternoon_char_vec, 
                                                  evening_char_vec, night_char_vec))]
personal_spotify_DT[1:6, .(end_time_dt, time_of_day_fct)]
```


## 5.2. Generate a bar plot with top 10 artists


```{r}
# prepare data: top_ten_listened_artists_by_play_time_DT
top_ten_listened_artists_by_play_time_DT <- 
  personal_spotify_DT[, .(total_song_play_time = sum(n_times_song_played_int)), 
                      by = .(artist_name)] %>% 
  # reorder by most played
  .[order(-total_song_play_time)] %>% 
  # take the top 10
  .[1:10] %>% 
  # add rank
  mutate(rank = 1:10, .before = artist_name)

# plot
p <- ggplot(top_ten_listened_artists_by_play_time_DT, 
       aes(x = reorder(artist_name, total_song_play_time), 
           fill = artist_name, y = total_song_play_time)) +
 geom_bar(stat = "identity") +
 geom_text(aes(label=format(total_song_play_time, big.mark=",")), # use format()
           vjust=.5, hjust = 1.2, 
           color="white", size = 3.5) +
 scale_fill_hue() +
 labs(y = "number of times played", x = "",
       title = " My 10 Most Listened Artists") +
 coord_flip() +
 theme_minimal() +
 theme(legend.position = "none") + 
 center_title
p

# interactive?
# ggplotly(p)
```

## 5.4. Visualize when you listened to music? On which days, on which times?


```{r}
p <- personal_spotify_DT[, .(songs_per_day = .N), by=.(date_dt, month_long_fct)] %>% 
  ggplot(aes(as.Date(date_dt), songs_per_day, color = month_long_fct)) + 
  geom_line(show.legend = F) +
  scale_x_date(date_breaks = "1 month", date_labels = "%B") +
  labs(x = "", y = "number of listened songs",
       title = "My Spotify listening history by day") + 
  theme_minimal() +
  center_title
p

# interactive?
# ggplotly(p, tooltip = c("y"))
```



```{r}
p <- personal_spotify_DT[, .N, by = .(date_dt, month_long_fct)] %>%  # total n songs per day
  .[, .(mean_n_songs = mean(N)), by = month_long_fct] %>%  # mean n songs per month
  ggplot(aes(x = month_long_fct, y = mean_n_songs, fill = month_long_fct)) +
  geom_bar(stat = "identity", show.legend = F) + 
  labs(x = "", y = "average number of listened songs",
      title = "My Spotify listening history by month") +
  theme_minimal() +
  center_title
p

# interactive?
# ggplotly(p, tooltip = "y")
```


```{r}
p <- personal_spotify_DT[, .N, by = .(date_dt, weekday_long_fct)] %>%  # total n songs per day
  .[, .(mean_n_songs = mean(N)), by = weekday_long_fct] %>%  # mean n songs per weekday
  ggplot(aes(x = weekday_long_fct, y= mean_n_songs, fill = weekday_long_fct)) +
  geom_bar(stat="identity", show.legend = F) + 
  labs(x = "", y = "average number of listened songs",
       title = "My Spotify listening history by weekday") +
  theme_minimal() +
  center_title
p

# interactive?
# ggplotly(p, tooltip = "y")
```


```{r}
p <- personal_spotify_DT[, .N, by = .(date_dt, time_of_day_fct)] %>%  # total n songs per day
  .[, .(mean_n_songs = mean(N)), by = time_of_day_fct] %>%  # mean n songs per time-of-day
  ggplot(aes(x= time_of_day_fct, y = mean_n_songs, fill = time_of_day_fct)) +
  geom_bar(stat="identity", show.legend = F) + 
  labs(x = "", y = "average number of listened songs",
       title = "My Spotify listening history by time of day") +
  theme_minimal() +
  center_title
p

# interactive?
# ggplotly(p, tooltip = "y")
```


```{r}
p <- personal_spotify_DT[, .N, by = .(date_dt, month_long_fct, weekday_long_fct)] %>%  # total
  .[, .(mean_n_songs = mean(N)), by = .(month_long_fct, weekday_long_fct)] %>%  # mean 
  ggplot(aes(x = fct_reorder(month_long_fct, desc(month_long_fct)), # reorder
             y = mean_n_songs, 
             fill = weekday_long_fct)) +
  geom_bar(stat = "identity", show.legend = T, position = "dodge") + 
  labs(x = "", y = "average number of listened songs",
       title = "My Spotify listening history by month and day",
       fill = "") + 
  coord_flip() +
  theme_minimal() +
  center_title
p

# interactive?
# ggplotly(p, tooltip = "y")
```


```{r}
p <- personal_spotify_DT[, .N, by = .(date_dt, weekday_long_fct, time_of_day_fct)] %>%  # total
  .[, .(mean_n_songs = mean(N)), by = .(weekday_long_fct, time_of_day_fct)] %>%  # mean 
  ggplot(aes(x = weekday_long_fct, y=mean_n_songs, fill = time_of_day_fct)) +
  geom_bar(stat="identity", show.legend = T) + 
  labs(x = "", y = "average number of listened songs",
       title = "My Spotify listening history by weekday and time of day", subtitle = "",
       fill = "Time of day:") +
  theme_minimal() +
  center_title +
  theme(axis.text.x = element_text(angle = 25)) # rotate x-axis text
p

# interactive?
# ggplotly(p, tooltip = "y")
```













# Part B: Popularity prediction using statistical methods (motivated Beginners + Advanced)

## Data: Kaggle Data

### 1. Split data into train / test sub-samples

* Useful for R: https://www.listendata.com/2015/02/splitting-data-into-training-and-test.html
* Useful for Python: https://www.journaldev.com/45019/split-data-into-training-testing-sets

```{r}
# subset vars: vars
vars <- c(
  "acousticness", "danceability",
  "duration_ms", "energy", "explicit", "instrumentalness",
  "liveness", "loudness",
  "speechiness", "tempo", "popularity"
)

# split into train/test data: train_index
set.seed(42)
train_index <- createDataPartition(spotify_DT$popularity, # dep. variable
                    p = .67, # % of data that goes to training set
                    list = F, # create matrix, not a list
                    times = 1
                    )

# split: train_DT, test_DT
train_DT <- spotify_DT[train_index, ..vars]
test_DT <- spotify_DT[-train_index, ..vars]

# row N
paste0("N obs. train: ", nrow(train_DT))
paste0("N obs. test: ", nrow(test_DT))
```

### 2.  Examine the correlation between the variables (train)

* 7 ways to do it: http://jamesmarquezportfolio.com/correlation_matrices_in_r.html

```{r}
train_DT %>% 
  cor() %>% # convert to correlation matrix
  ggcorrplot(lab = T, digits = 1, lab_size = 3, tl.cex = 8)
```


### 3. First predictions with simple regression models (train)

* Useful: https://analyticsindiamag.com/how-to-code-linear-regression-models-with-r/

```{r, warning=F, message=F, results="asis"}
# fit / train a linear model
# note: https://analyticsindiamag.com/how-to-code-linear-regression-models-with-r/
model_1 <- lm(formula = popularity ~ ., data = train_DT) # fit a model

# reveal model equation
extract_eq(model_1, wrap = T)
```


```{r, warning=FALSE, message=FALSE, include=F}
# reveal model
stargazer(model_1, type = "text", omit = "Constant", ci=T)
```


```{r}
# alternatively
modelsummary(models = list("Popularity" = model_1),
  estimate = c("{estimate}{stars}"),
  statistic = "conf.int",
  coef_omit = "Intercept"
)
```

### 4. From training to testing – making predictions

```{r}
# predictions on test data
test_DT[, predicted_popularity := predict(model_1, test_DT)]
test_DT[, abs_error := abs(popularity - predicted_popularity)]
test_DT[, .(popularity, predicted_popularity, abs_error)][1:6]

# RMSE for test data: rmse_test
rmse_test <- Metrics::rmse(actual = test_DT$popularity, 
              predicted = test_DT$predicted_popularity) %>% 
  round(digits = 3)
paste0("RMSE for test data: ", rmse_test)
```



### 5. Apply advanced machine learning algorithms

* Let the student decide…


